---
title: "Bitcoin price fluctuation with Twitter text analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
load("datas.RData")
library(tidytext) 
library(ggplot2)
library(RColorBrewer)
library(wordcloud)
library(tm)
library(twitteR)
library(ROAuth)
library(plyr)
library(stringr)
library(base64enc)
library(dplyr)
library(tidyr)
library(rtweet)

```

## Abstract
In this project, I applied text analysis to find the relations between ”people’s behavior on twitter” and ”Bitcoin’s price and volume.” Since it is a less-than-one-month project and Twitter set the limit rate for retrieving data via API, the comparison only covered data of three weeks.   


## Bitcoin Historical Price
```{r echo=FALSE, message = FALSE}

ts.price
```

## Bitcoin Historical Trading Volume
The two peaks occurring at 4/10~4/11 and 4/22~4/23 are noteworthy. We can focus on these two dates in the below word frequency analysis and word clouds.  

```{r echo=FALSE}
ts.volume
```


## Word Frequency from 4/13 to 5/2 {.tabset .tabset-fade}
### 4/13 
```{r echo=FALSE}
bp.words.0413
```

### 4/14
```{r echo=FALSE}
bp.words.0414
```

### 4/15
```{r echo=FALSE}
bp.words.0415
```

### 4/16
```{r echo=FALSE}
bp.words.0416
```

### 4/17
```{r echo=FALSE}
bp.words.0417
```

### 4/18
```{r echo=FALSE}
bp.words.0418
```

### 4/19
```{r echo=FALSE}
bp.words.0419
```

### 4/20
```{r echo=FALSE}
bp.words.0420
```

### 4/21
```{r echo=FALSE}
bp.words.0421
```

### 4/22
```{r echo=FALSE}
bp.words.0422
```

### 4/23
```{r echo=FALSE}
bp.words.0423
```

### 4/24
```{r echo=FALSE}
bp.words.0424
```

### 4/25
```{r echo=FALSE}
bp.words.0425
```

### 4/26
```{r echo=FALSE}
bp.words.0426
```

### 4/27
```{r echo=FALSE}
bp.words.0427
```

### 4/28
```{r echo=FALSE}
bp.words.0428
```

### 4/29
```{r echo=FALSE}
bp.words.0429
```

### 4/30
```{r echo=FALSE}
bp.words.0430
```

### 5/01
```{r echo=FALSE}
bp.words.0501
```

### 5/02
```{r echo=FALSE}
bp.words.0502
```
##


## Word Cloud from 4/13 to 5/2 {.tabset .tabset-fade}
### 4/13
```{r echo=FALSE}
wordcloud(tweet_words_0413$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/14
```{r echo=FALSE}
wordcloud(tweet_words_0414$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/15
```{r echo=FALSE}
wordcloud(tweet_words_0415$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/16
```{r echo=FALSE}
wordcloud(tweet_words_0416$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```


### 4/17
```{r echo=FALSE}
wordcloud(tweet_words_0417$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/18
```{r echo=FALSE}
wordcloud(tweet_words_0418$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/19
```{r echo=FALSE}
wordcloud(tweet_words_0419$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/20
```{r echo=FALSE}
wordcloud(tweet_words_0420$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/21
```{r echo=FALSE}
wordcloud(tweet_words_0421$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/22
```{r echo=FALSE}
wordcloud(tweet_words_0422$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/23
```{r echo=FALSE}
wordcloud(tweet_words_0423$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/24
```{r echo=FALSE}
wordcloud(tweet_words_0424$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/25
```{r echo=FALSE}
wordcloud(tweet_words_0425$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/26
```{r echo=FALSE}
wordcloud(tweet_words_0426$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/27
```{r echo=FALSE}
wordcloud(tweet_words_0427$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/28
```{r echo=FALSE}
wordcloud(tweet_words_0428$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/29
```{r echo=FALSE}
wordcloud(tweet_words_0429$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 4/30
```{r echo=FALSE}
wordcloud(tweet_words_0430$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

### 5/01
```{r echo=FALSE}
wordcloud(tweet_words_0501$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```


### 5/02
```{r echo=FALSE}
wordcloud(tweet_words_0502$word, min.freq = 20,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

##